The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-03-11 src/ms.tex
numbers

As an example of this effect within the \astropy Project, here we focus on
contributions made to the \astropypkg core package.
Figure~\ref{fig:contributor-summary:Ncommitters} shows the number of
contributors who have contributed a given fraction of the total number of Git
commits, separated into three separate ``eras'' in the history of the
Project.\footnote{Note, however, that measuring these statistics in terms of Git
commits is not a perfect way of encapsulating ``effort,'' but we use this metric
for its simplicity and clear definition.}
The annotations show that, within the early (July 2011--January 2015), mid
(January 2015--June 2018), and recent (June 2018--November 2021) eras, 90\% of
the commits to the \astropypkg core package have come from 18, 34, and 44
contributors.
While the trend is encouraging --- a larger pool of contributors are
contributing more, fractionally --- this emphasizes that, still, the vast
majority of the work in \astropypkg is done my a small subset of the
contributors.

>>>>

As an example of this within the \astropy Project, here we focus on
contributions made to the \astropypkg core package.
Figure~\ref{fig:contributor-summary:Ncommitters} shows the number of
contributors who have contributed a given fraction of the total number of Git
commits, separated into three separate time spans (``eras'') in the history of
the Project.\footnote{Note, however, that measuring these statistics in terms of
Git commits is not a perfect way of encapsulating ``effort,'' but we use this
metric for its simplicity and clear definition.}
The annotations show that, within the early (July 2011--January 2015), mid
(January 2015--June 2018), and recent (June 2018--November 2021) eras, 90\% of
the commits to the \astropypkg core package have come from 18, 34, and 44
contributors.
While the trend is encouraging --- a larger pool of contributors are
contributing more, fractionally --- this emphasizes that, still, the vast
majority of the work in \astropypkg is done my a small subset ($<20\%$) of the
115, 216, and 234 contributors, respectively, within each era.

Since its inception, the most active contributors to the \astropypkg package
have spanned a range of career stages and career paths.
